---
title: "titulo do meu arquivo"
author: "meu nome"
format: html
editor: visual
---

## Quarto

*Quarto* enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

```{r}

```

...{r} library(tidyverse) library(palmerpenguins) ...

...{r} penguins \|\> ggplot() + aes(x = flipper_length_mm, y = body_mass_g) + geom_point(aes(color = species, shape = species)) + scale_color_manual(values = c("darkorange", "darkorchid", "cyan4")) + theme_minimal() ...

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

library(palmerpenguins) penguins \|\> ggplot() + aes(x = flipper_length_mm, y = body_mass_g) + geom_point(aes(color = species, shape = species)) + scale_color_manual(values = c("darkorange", "darkorchid", "cyan4")) + theme_minimal()
